Undirected Graph Exploration with $\Theta(\log\log n)$ Pebbles

### 2016-05-10 presentation/main.tex
barriers

\section{Pebble simulation}
\begin{frame}
  \begin{theorem}
    There is a constant $c\in\mathcal{N}$, such that for any Graph $G$
    with bounded degree and any $(s,p,2m)$ pebble machine $\mathcal{M}$, there
    exists a $(cs,p+c,m)$ pebble machine $\mathcal{M}'$ that simulates the walk
    of $\mathcal{M}$ or explores $G$.
  \end{theorem}
\end{frame}

\begin{frame}
  \frametitle{Tape simulation via pebbles}
  \begin{itemize}
    \item Simulate tape of size $m$ by pebbles:
      \begin{itemize}
        \item<3-> Separate into memory blocks of size $m_{1}$
        \item<4-> Represent every block by one of $\left\{p_{0},\dots,p_{\frac{m}{m_{1}}-1}\right\}$ pebbles
      \end{itemize}
  \end{itemize}
  \uncover<2->{\input{tikz/tapesimint}}
\end{frame}

@@

\begin{frame}
  \frametitle{Recall: Mechanisms of simulation}
  \begin{itemize}
    \item Simulation of $M_{\text{Walk}}$ which explores at least $2^{m_{1}}$
      distinct vertices \uncover<2->{\checkmark}
    \item Identify \emph{distinct} vertices of the walk \uncover<3->{\checkmark}
    \item Read from and write to simulated tape \uncover<4->{\checkmark}
    \item Preserve tape content through steps of simulated agent \uncover<5->{\checkmark}
  \end{itemize}
  \uncover<6->{
    \begin{theorem}
      There is a constant $c\in\mathcal{N}$, such that for any Graph $G$
      with bounded degree and any $(s,p,2m)$ pebble machine $\mathcal{M}$, there
      exists a $(cs,p+c,m)$ pebble machine $\mathcal{M}'$ that simulates the walk
      of $\mathcal{M}$ or explores $G$.
    \end{theorem}
  }
\end{frame}

@@

\section{Limitations of pebble machines}
\begin{frame}
  \frametitle{Limitations of pebbles}
  \begin{itemize}
    \item Construct graphs which cannot be traversed by agents with $p$ pebbles
    \item Such graphs are called $p$-barriers
      \begin{center}
        \resizebox{0.3\textwidth}{!}{\input{tikz/barrier}}
      \end{center}
    \item In the following: inductive construction of barriers
  \end{itemize}
\end{frame}

>>>>

\section{Pebble simulation}
\begin{frame}
  \begin{theorem}
    There is a constant $c\in\mathbb{N}$, such that for any Graph $G$
    with bounded degree and any $(s,p,2m)$ pebble machine $\mathcal{M}$, there
    exists a $(cs,p+c,m)$ pebble machine $\mathcal{M}'$ that simulates the walk
    of $\mathcal{M}$ or explores $G$.
  \end{theorem}
\end{frame}

\begin{frame}
  \frametitle{Tape simulation via pebbles}
  \begin{itemize}
    \item Simulate tape of size $m$ by pebbles:
      \begin{itemize}
        \item<3-> Separate into memory blocks of size $m_{1}$
        \item<4-> Represent every block by one of
          $p_{0},\dots,p_{\frac{m}{m_{1}}-1}$ pebbles
      \end{itemize}
  \end{itemize}
  \uncover<2->{\input{tikz/tapesimint}}
\end{frame}

@@

\begin{frame}
  \frametitle{Recall: Mechanisms of simulation}
  \begin{itemize}
    \item Simulation of $M_{\text{Walk}}$ which explores at least $2^{m_{1}}$
      distinct vertices \uncover<2->{\checkmark}
    \item Identify \emph{distinct} vertices of the walk
      \uncover<3->{\checkmark}
    \item Read from and write to simulated tape \uncover<4->{\checkmark}
    \item Preserve tape content through steps of simulated agent
      \uncover<5->{\checkmark}
  \end{itemize}
  \uncover<6->{
    \begin{theorem}
      There is a constant $c\in\mathbb{N}$, such that for any Graph $G$
      with bounded degree and any $(s,p,2m)$ pebble machine $\mathcal{M}$,
      there exists a $(cs,p+c,m)$ pebble machine $\mathcal{M}'$ that simulates
      the walk of $\mathcal{M}$ or explores $G$.
    \end{theorem}
  }
\end{frame}

@@

\section{Limitations of pebble machines}
\begin{frame}
  \frametitle{Limitations of pebbles}
  \begin{itemize}
    \item Construct 3-regular graphs which cannot be traversed by an agent
      $\mathcal{A}$ with $p$ pebbles
    \item Such graphs are called $p$-barriers
      \begin{center}
        \resizebox{0.7\textwidth}{!}{\input{tikz/barrierint}}
      \end{center}
    \item If $\mathcal{A}$ starts in any vertex in $G$ it will never traverse
      the barrier from $v_{1}$ ($v_{2}$) to $v_{2}$ or $v_{3}$ using at most
      $p$ pebbles
  \end{itemize}
\end{frame}
